---
title: "Optimism Pilot Study"
author: "Susi Zajitschek"
date: "17 April 2019"
output: 
  html_document:
    code_download: true
    code_folding: hide
    depth: 4
    number_sections: no
    theme:  flatly
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  cache = TRUE,
  tidy = TRUE
)
```
# Load data
```{r}
opt <- read.csv(file = "OptNewB.csv")
str(opt)
#size<- read.csv(file = "data/Size fish optimism.csv" # already
#opt$size <- size$size[match(opt$Fish_ID, size$Fish_ID)]
```



#Add a Charater variable for each week
```{r}
Opt <- opt 
  #mutate(weekB = sprintf("%s-%s", "Week", Week))
  Opt$Week <- as.character(Opt$Week)
#str(Opt)

```
Packages loaded
```{r include=FALSE}
library(dplyr)
library(tidyverse)
library(lme4)
library(ggplot2) 
library(DHARMa)
library(multcomp)
library(lmerTest)
library(ggbeeswarm)
library(rptR)
library(kableExtra)
# Hamza's summary tables: sjPlot
library(sjPlot) #use: tab_model() ...
```

## Main variable 
I have tested all possible variables, but this seemed most meaningful: 
### Time very near to stimulus
```{r}

opt2 = lmer(data=Opt, (Time5cm) ~ (1|Fish_ID) + Treat * Week + video + First + Size + Sex )
anova(opt2)

summary(glht(opt2, linfct=mcp(Week="Tukey")))
summary(glht(opt2, linfct=mcp(Treat="Tukey")))
tab_model(opt2)

opt3 = lmer(data=Opt, (Time5cm) ~ (1|Fish_ID) + Treat  )
anova(opt3)
tab_model(opt3)
```

Normatlity check (not great, but better than all possible transformations)

```{r}
qqnorm(resid(opt2)) # skewed but ok // better than transformed versions...
# check model assumptions

simulationOpt2 <- simulateResiduals(fittedModel = opt2, n = 250) #n controls the number of simulations
#plot(simulationOpt2)
#plot(simulateResiduals(simulationOpt2))
```

PLOT: Beeswarm / Forest with box overlay
```{r}
forest.plot.T5cm <- opt %>%
  
  mutate(Treat = factor(Treat, levels = c("Pos", "Amb", "Neg"))) %>%
  ggplot(aes(x = Treat, y = Time5cm, colour = Treat, fill = Treat)) + 
  geom_hline(yintercept = 0, linetype = 2) + 
  geom_hline(yintercept = 0.23, linetype = 2, colour = "steelblue", size = 1) +
  geom_quasirandom(data = opt %>% 
                     mutate(Treat = factor(Treat, levels = c("Pos", "Amb", "Neg"))),
                   aes(x = Treat, y = Time5cm), alpha=0.4) +
  #geom_errorbar(mapping = aes(ymin = LCI, ymax = UCI), width = 0, position = pd, size=1, colour = "grey10") + 
  #geom_point( size=3.25, shape = 23, stroke = .75, color = "grey10") +  #position = pd,
 
  ylab("Time spent closest to screen [0-5cm] ") +
  theme_minimal(14) +
  theme(panel.grid.major.y = element_blank(), 
        panel.grid.minor.y = element_blank(), 
        legend.position = "none",
        axis.text.y = element_text(size = 13, hjust = 1)) +
  scale_color_manual(values = c("Neg" = "#a50f15", "Amb" = "#fe9929", "Pos" = "#4daf4a"), 
                     #name = "Relationship\nto fitness")+
  scale_fill_manual(values = c("Neg" = "#a50f15", "Amb" = "#fe9929", "Pos" = "#4daf4a")))

forest.plot.T5cm +  geom_boxplot(fill= NA, notch = TRUE )
```

Individual variation plot
```{r}
Time5cm.plot <- opt %>% 
  mutate(Treat = factor(Treat, levels = c("Pos", "Amb", "Neg"))) %>%
  group_by(Sex, Fish_ID, Treat) %>% 
  summarise(TimeNearestStimulus = mean(Time5cm, na.rm = TRUE)) %>% 
  ggplot(aes(Treat, TimeNearestStimulus, group = Fish_ID, colour = factor(Fish_ID))) +
  geom_line(alpha = 0.3) + 
  theme(legend.position="none") +
  facet_grid(Sex ~ .) +
  labs(title = "Time spent within 5cm from Stimulus")

Time5cm.plot
```

##Repeatability
## for each fish, separately for each stimulus
```{r}
OptN <- subset(Opt, Treat == "Neg") 
OptP <- subset(Opt, Treat == "Pos") 
OptA <- subset(Opt, Treat == "Amb") 

citation("rptR")

rpt(Time5cm ~ (1 | Fish_ID) , grname = "Fish_ID", data = OptN, datatype = "Gaussian", 
      nboot = 0, npermut = 0)      #R=0.103
  
rpt(Time5cm ~ (1 | Fish_ID), grname = "Fish_ID", data = OptP, datatype = "Gaussian", 
    nboot = 0, npermut = 0)   #R=0.148

rpt(Time5cm ~ (1 | Fish_ID), grname = "Fish_ID", data = OptA, datatype = "Gaussian", 
    nboot = 0, npermut = 0)   #R=0.213
```

across weeks (but not taking order into account (?)
```{r}
cmStim <- rpt(Time5cm ~ Treat + Week + First + Size + Sex + video+ (1 | Fish_ID), grname = "Fish_ID", data = opt, datatype = "Gaussian", nboot = 0, npermut = 0)
summary(cmStim)
str(opt)

```

```{r}
#Across weeks
Time5cm.plot <- Opt %>% 
  mutate(Week = factor(Week, levels = c("1", "2", "3"))) %>%
  group_by(Sex, Fish_ID, Treat, Week) %>% 
  #summarise(TimeNearestStimulus = mean(Time5cm, na.rm = TRUE)) %>% 
  ggplot(aes(Week, Time5cm, group = Fish_ID, colour = factor(Fish_ID))) +
  geom_line(alpha = 0.3) +
  theme(legend.position="none") +
  facet_grid(Treat ~ . ) +
  
  labs(title = "Time spent within 5cm from Stimulus")

Time5cm.plot
```
# ok, so what does this all show me?
Ambigous cues lie in the middle between positive and negative cues.
Animals spend less time close to negative cue than at positive one.

Effect seems to be most repeatable (consistent?) for ambigous cues: r=0.21.

What do I want to know?

# HAMZA: ignore below. 
I spend a lot of time trying to come u with different indices, that just doesn't work...


# Optimism Index
### for time spent very near stimulus
Fish that are >0.5 are optimistic, Fish <0.5 pessimistic

## (time spent close to ambig – time spent close to neg) / (time spent close to pos – time spent close to neg)
```{r eval=FALSE, include=FALSE}
optindex3  <- opt %>%
  mutate(sqrt5cm = sqrt(Time5cm)) %>%
  dplyr::select( Fish_ID, Week, Treat, sqrt5cm )  %>% # sqrt5cm
  spread(Treat, sqrt5cm) %>%
  mutate( (Amb-Neg)/(Pos-Neg))
optindex3

colnames(optindex3)
optindex3 <- optindex3 %>% rename(index = "(Amb - Neg)/(Pos - Neg)")
colnames(optindex3)

nrow(optindex3[optindex3$index > 0.5, ]) # 385
nrow(optindex3[optindex3$index < 0.5, ]) #  115

nrow(optindex3raw$index = "NaN") 
sum(is.na(optindex3raw$index)) #16
sum(is.na(optindex3log$index)) #46
sum(is.na(optindex3$index)) #0

```

repeatability of the optimism indx
across weeks (but not taking order into account (?) 
NO SENSIBLE RESULT. 

```{r eval=FALSE, include=FALSE}
optindex4  <- optindex3 %>%
  unite_("Fish", c("Fish_ID", "Week"), remove = FALSE)

optind <- optindex4[ !(optindex4$Fish %in% c("26_3","30_2","52_1","55_1", "82_2", "83_1", "93_3", "94_3", "95_3", "112_3", "113_1", "115_1", "115_2", "116_3", "123_2", "126_3", "127_1", "133_3", "139_2", "143_2","147_2", "155_2" )), ]

ind <- rpt(index ~   (1 | Fish_ID), grname = "Fish_ID", data = optind, datatype = "Gaussian", nboot = 0, npermut = 0) 
summary(ind)
tab_model(ind)

rpt(index ~ (1 | Fish_ID), grname = "Fish_ID", data = optind, datatype = "Gaussian", 
      nboot = 0, npermut = 0) #doesn't work
```
But maybe plot the indices?

FIRST, take RELATIVE time :percentage of time spent in pos/amb/neg:
i.e. each column: (x/180)*100


```{r eval=FALSE, include=FALSE}
optindex3$AmbP <- (optindex3$Amb / 180)*100
optindex3$NegP <- (optindex3$Neg / 180)*100
optindex3$PosP <- (optindex3$Pos / 180)*100

optindex3b  <- optindex3 %>%
  mutate( (Amb/(Amb+Neg+Pos)-(Neg/(Amb+Neg+Pos)))/(Pos/(Amb+Neg+Pos)-Neg/(Amb+Neg+Pos)))
optindex3b


```

Plot idex across weeks
```{r eval=FALSE, include=FALSE}
Time5cm.index.plot <- optindex3 %>% 
  ggplot(aes(Week, index, group = Fish_ID, colour = factor(Fish_ID))) +
  geom_point(alpha = 0.3) +
  geom_line(alpha = 0.3) +
  theme(legend.position="none") +
  labs(title = "Time spent within 5cm from Stimulus")

Time5cm.index.plot
```
ok, that's shit, still... 


```{r eval=FALSE, include=FALSE}
hist(optind$index)
optind$index2 <- optind$index^2
```

SO TRY DISTANCE TRAVELLED

#Optimism Index
## for TOTAL DISTANCE TRAVELLED
Fish that are >0.5 are optimistic, Fish <0.5 pessimistic

## 
```{r eval=FALSE, include=FALSE}
optDist  <- opt %>%
 # mutate(dist = sqrt(Time5cm)) %>%
  dplyr::select( Fish_ID, Week, Treat, TotalDist)  %>%
  spread(Treat, TotalDist) %>%
  mutate( (Amb-Neg)/(Pos-Neg))
optDist

names(optDist)[6] <- "indexD"

nrow(optDist[optDist$indexD > 0.5, ]) # 326
nrow(optDist[optDist$indexD < 0.5, ]) #  158

```

repeatability of the optimism indx
across weeks (but not taking order into account (?)
```{r eval=FALSE, include=FALSE}
optindex4  <- optindex3 %>%
  unite_("Fish", c("Fish_ID", "Week"), remove = FALSE)

optind <- optindex4[ !(optindex4$Fish %in% c("26_3","30_2","52_1","55_1", "82_2", "83_1", "93_3", "94_3", "95_3", "112_3", "113_1", "115_1", "115_2", "116_3", "123_2", "126_3", "127_1", "133_3", "139_2", "143_2","147_2", "155_2" )), ]

ind <- rpt(indexD ~   (1 | Fish_ID), grname = "Fish_ID", data = optDist, datatype = "Gaussian", nboot = 0, npermut = 0) 
summary(ind)

rpt(index ~ (1 | Fish_ID), grname = "Fish_ID", data = optind, datatype = "Gaussian", 
      nboot = 0, npermut = 0) #doesn't work
```

Plot idex across weeks
```{r eval=FALSE, include=FALSE}
Time5cm.index.plot <- optind %>% 
  ggplot(aes(Week, index, group = Fish_ID, colour = factor(Fish_ID))) +
  geom_line(alpha = 0.3) +
  theme(legend.position="none") +
  labs(title = "Time spent within 5cm from Stimulus")

Time5cm.index.plot
```
ok, that's shit, so far...
```{r eval=FALSE, include=FALSE}
kable(cbind (optindex2,optindex2)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```

```{r eval=FALSE, include=FALSE}
neutral <- filter(optindex2, index > 0.4, index < 0.6) #52 obs

noextremes <- filter(optindex2, index > -10, index < 10)
```

```{r eval=FALSE, include=FALSE}
Time5cm.index.plot <- noextremes %>% 
  ggplot(aes(Week, index, group = Fish_ID, colour = factor(Fish_ID))) +
  geom_line(alpha = 0.3) +
  theme(legend.position="none") +
  labs(title = "Time spent within 5cm from Stimulus")

Time5cm.index.plot
```


index on distance
remove non-moving fish
sqroot 